Inference of proto-neutron star properties from gravitational wave data in core-collapse supernovae.

### 2020-09-23 methods.tex
update

\pcd{To build the model of the ratio $r$ as a function of the frequency $f$ we use the 
spherically symetric (1D) simulations of the {\it model set}. Figure~\ref{fig:LMVAR}
shows the data for the $25$ numerical simulations. As identified by \cite{Torres:2019b}, the only systematic
deviation from a single universal relation is the numerical code used in the simulations. 
To avoid any systematic effect, we only use to build our model the $18$ simulations performed with the ALCAR-AENUS
code, which is the same code that was used in our test set. The consequences of this choice are discussed in the
conclusions. Using this data, we} parametrize the ratio with a cubic polynomial
regression with heteroscedastic errors
%Here we are using the data from \textcolor{red}{only {\sc AENUS-ALCAR} or both?, maybe colour-code the two groups of data points } to fit a cubic polyn

@@

\pcd{We use this model to infer the properties of the simulations in the 
{\it test set} described in in Section \ref{sec:simulations}.}
To develop \pcd{and describe} the method we \pcd{\sout{considered} focus on} the gravitational wave signal
\pcd{of} {\texttt s20S}, originally
sampled at 16384 Hz but resampled at 4096 Hz.
A spectrogram of this signal is shown in Figure \ref{fig:spectrogram} based on
autoregressive estimates \pcd{[CITATION?]}of the local spectra for successive time intervals of 
\textcolor{red}{length 200} with a \textcolor{red}{ 90\%} overlap.
The dominant emission mode corresponds to the PNS oscillation $\mbox{}^2 g_2$-mode. We have
developed a time-frequency method to track the ridge $m(t)$ in the spectrogram,
taking into account that it is monotonically increasing as time goes. 
\pcd{This is a property of the $\mbox{}^2 g_2$-mode, the frequency of which  
increases as the object becomes more massive and compact}.
Starting from either the left- or right-most column of the time-frequency matrix
we identify and trace the sequence of amplitude peaks within a certain frequency
band given the monotonicity constraint. Appendix \ref{app:gmode} is providing more
details on the reconstruction of the $g$ mode ridge.

@@

\begin{figure}
 \centering
 \includegraphics[width=0.5\textwidth,height=0.3\textheight]{plots/ratio}
 \caption{Ratio $M_{\rm PNS}/R_{\rm PNS}^2$ as function of time extracted from the $\mbox{}^2 g_2$-mode of the {\texttt s20S} signal (red points and the 95\% confidence belt in grey) compared to the ratio value derived from the PNS mass and radius given by the simulation code (black points).} \label{fig:ratio}
\end{figure}

>>>>

\pcd{To build the model of the ratio $r$ as a function of the frequency $f$ we use the 
spherically symetric (1D) simulations of the {\it model set}. Figure~\ref{fig:LMVAR}
shows the data for the $25$ numerical simulations. As identified by \cite{Torres:2019b}, the only systematic
deviation from a single universal relation is the numerical code used in the simulations. 
To avoid any systematic effect, we only use the $18$ simulations performed with the ALCAR-AENUS
code, which is the same code that was used in our test set. The consequences of this choice are discussed in the
conclusions. Using this data, we} parametrize the ratio with a cubic polynomial
regression with heteroscedastic errors
%Here we are using the data from \textcolor{red}{only {\sc AENUS-ALCAR} or both?, maybe colour-code the two groups of data points } to fit a cubic polyn

@@

\pcd{We use this model to infer the properties of the simulations in the 
{\it test set} described in in Section \ref{sec:simulations}.}
To describe the method we focus on the gravitational wave signal
of {\texttt s20S}, originally
sampled at 16384 Hz but resampled at 4096 Hz.
A spectrogram of this signal is shown in Figure \ref{fig:spectrogram} based on
autoregressive estimates \pcd{[CITATION?]}of the local spectra for successive time intervals of 
\textcolor{red}{length 200} with a \textcolor{red}{ 90\%} overlap.
The dominant emission mode corresponds to the PNS oscillation $\mbox{}^2 g_2$-mode. We have
developed a time-frequency method to track the ridge $m(t)$ in the spectrogram,
taking into account that it is monotonically increasing as time goes. 
\pcd{This is a property of the $\mbox{}^2 g_2$-mode, the frequency of which  
increases as the object becomes more massive and compact}.
Starting from either the left- or right-most column of the time-frequency matrix
we identify and trace the sequence of amplitude peaks within a certain frequency
band given the monotonicity constraint. Appendix \ref{app:gmode} is providing more
details on the reconstruction of the $g$ mode ridge.

@@

\begin{figure}
 \centering
 \includegraphics[width=0.5\textwidth,height=0.3\textheight]{plots/ratio}
 \caption{Ratio $M_{\rm PNS}/R_{\rm PNS}^2$ as function of time extracted from the $\mbox{}^2 g_2$-mode of the {\texttt s20S} signal (red points and the 95\% confidence belt in grey) compared to the ratio value derived from the PNS mass and radius given by the simulation code (black points) \mab{To be redone in python}.} \label{fig:ratio}
\end{figure}
